Mermory-efficient Fujisaki-Okamoto transformation

### 2024-05-20 lattices/compact-fo-using-mac/manuscript/main.tex
checkpoint

    % TODO: in game 3, the challenge encryption is done using a truly random MAC key
    %   talk about QUERY*

>>>>

    In game 3, the challenge encryption routine is modified. Instead of computing a pseudorandom MAC key $k^\ast \leftarrow G(m^\ast)$, a truly random MAC key is sampled uniformly from the message space $k^\ast \leftsample \mathcal{K}_\text{MAC}$. Under the random oracle model, game 3 and game 2 are indistinguishable from the adversary's perspective unless it makes a hash query on the value of $m^\ast$. Denote the probability that the adversary makes a hash query on $m^\ast$ by $P[\operatorname{QUERY}\ast]$, then:

    \begin{equation*}
        \epsilon_2 - \epsilon_3 \leq P[\operatorname{QUERY}\ast]
    \end{equation*}

    % TODO: Bound the probabiolity P[QUERY*]
